cpcrw_ms

### 2015-12-19 manuscript/cpcrw_manuscript.Rmd
Outlier exclusion citation
Thinking about possible tables and figures

Analysis. Outlier exclusion.

@@

>>>>

AOutlier exclusion based on 3.2 mean absolute deviations from treatment and temperature mean. We excluded X of Y (Z%) of the summarized samples for this reason.

Citation: Davies, P.L. and Gather, U. (1993). "The identification of multiple outliers" (with discussion). J. Amer. Statist. Assoc., 88, 782-801.

nalysis. Outlier exclusion.

@@

Table X. Summary of treatment effects on gas fluxes.

Figure X. A faceted (Temperature ~ Treatment) plot showing fnormalized lux means and errors by incubation time.
 (Basically the figure already in the README diagnostics.)
TFigur X. 
Core water content across the course of the experiment. (Basically the figure already in the README diagnostics.)
